Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor periodic systems

### 2013-10-04 python-simulation/paper-paedf/paper-paedf.tex
added content to tex

        A scheduling policy is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are released and unfinished jobs present in the system. It is said to be \textbf{preemptive} if it allows the processor to begin computation of a new job when the currently computed job is still unfinished.\\

@@

\section{Performance of EDF with preemption cost}

@@

@@

\section{PA-EDF: an amelioration}

>>>>

        A scheduling policy (or \emph{algorithm}) is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are released and unfinished jobs present in the system. It is said to be \textbf{preemptive} if it allows the processor to begin computation of a new job when the currently computed job is still unfinished.\\

@@

\section{Performance of EDF with preemption cost}
% Rename section to something like "Old results do not old, bitch"

@@

        \subsubsection{Longer transitive period}
        Consider the following system

        \begin{center}
            \begin{tabular}{|r|c|c|c|c|c|}
                \hline
                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
                $\tau_1$    & 0     & 5     & 10   & 10    & 1     \\ \hline
                $\tau_2$    & 4     & 1     & 1    & 10    & 1     \\ \hline
                $\tau_3$    & 6     & 4     & 10   & 10    & 1     \\ \hline
            \end{tabular}
        \end{center}

        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet. This only happens at instant $O_{max} + 4 \cdot H$.\\

        Figure.

        \subsubsection{Deadline miss in transitive, not in periodic}

    In this section, we present other results which do not hold under the costly preemption assumption.

        \subsubsection{Idling dominate non-idling}

@@

        \begin{center}
            \begin{tabular}{|r|c|c|c|c|c|}
                \hline
                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
                $\tau_1$    & 0     & 3     & 8    & 8     & 2     \\ \hline
                $\tau_2$    & 0     & 3     & 5    & 8     & 2     \\ \hline
                $\tau_3$    & 1     & 1     & 1    & 8     & 2     \\ \hline
            \end{tabular}
        \end{center}

        And consider the following schedule which shows that it is feasible with an idling scheduling policy.

        [figure]

        However, it is easy to see that no non-idling algorithm can successfully schedule this system: at $t=0$, a non-idling algorithm has to choose between the first job of $\tau_1$ and $\tau_2$ for execution, whichever is chosen will then be preempted by the first job of $\tau_3$ (if not, it will miss its deadline in $t=2$). Then, at $t=2$, there will be $3+2+2=7$ units of computation left to compute before the deadline at $t=8$, the system will thus certainly miss a deadline.

        \subsubsection{Dynamic dominate fixed-job}

        \subsubsection{u < 0.69 is not sufficient}

        \subsubsection{Require Claivoyance}

        \subsubsection{Preemption can happen anywhere}

\section{PA-EDF: an extension of EDF for costly preemption}
